---
title: "3D Operations using `dddr`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{operations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8,
  fig.height=5
)
```

```{r setup, message=FALSE}
library(dplyr)
library(ggplot2)
library(dddr)
```

The R package `dddr` works well with three-diensional spatial data. It gives three-dimensional objects like points, velocities, and rotations first-class vector status in R, enabling usage as column types within `data.frame` and `tibble`.

# Vector Mathematics

Vectors have addition and subtraction operations, as well as scalar multiplication.

```{R}
spiral <- data.frame(i = seq(0, 10*pi, by=0.05)) %>%
  mutate(
    # vector3s are created using three numeric vector arguments,
    # and thanks to dplyr, can refer to other columns in the dataframe
    circular_part = vector3(x=cos(i), y=sin(i), z=0),
    forward_part = vector3(x=0, y=0, z=i/15),
    # vector3s can be added together and multiplied by numerics 
    spiral_part = circular_part * i / 30 + forward_part
  )

ggplot(spiral, aes(x=spiral_part$x, y=spiral_part$y)) +
  geom_point() +
  geom_path() +
  coord_equal()
```

```{R}
spiral %>%
  mutate(addition_example = spiral_part + vector3(1, 1, 0)) %>%
  ggplot() +
  geom_point(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_path(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_point(aes(x=addition_example$x, y=addition_example$y), color="blue") +
  geom_path(aes(x=addition_example$x, y=addition_example$y), color="blue") +
  coord_equal()
```

```{R}
spiral %>%
  mutate(multiplication_example = spiral_part * 1.5) %>%
  ggplot() +
  geom_point(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_path(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_point(aes(x=multiplication_example$x, y=multiplication_example$y), color="blue") +
  geom_path(aes(x=multiplication_example$x, y=multiplication_example$y), color="blue") +
  coord_equal()
```

# Rotations

Vectors can be rotated using the `rotate` function in many different ways. One approach is a very simple axis-angle.

```{R}
spiral %>%
  mutate(axis_angle_rotation = rotate(spiral_part, axis=vector3(0, 1, 0), angle=pi/4)) %>%
  ggplot() +
  geom_point(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_path(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_point(aes(x=axis_angle_rotation$x, y=axis_angle_rotation$y), color="blue") +
  geom_path(aes(x=axis_angle_rotation$x, y=axis_angle_rotation$y), color="blue") +
  coord_equal()
```

Another approach uses from/to specific vectors.

```{R}
spiral %>%
  mutate(from_to_rotation = rotate(spiral_part, from=vector3(0, 0, 1), to=vector3(-1, -1, -1))) %>%
  ggplot() +
  geom_point(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_path(aes(x=spiral_part$x, y=spiral_part$y), color="black") +
  geom_point(aes(x=from_to_rotation$x, y=from_to_rotation$y), color="blue") +
  geom_path(aes(x=from_to_rotation$x, y=from_to_rotation$y), color="blue") +
  coord_equal()
```

# Spatial Functions

There are a handful of other useful functions, including `angle_between`, and vector projection and rejection.

```{R}
spiral %>%
  mutate(angle = angle_between(spiral_part, vector3(0, 0, 0), origin=vector3(0, -2, 0))) %>%
  ggplot() +
  geom_point(aes(x=i, y=angle)) +
  geom_line(aes(x=i, y=angle))
```





