---
title: "vrmvrm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vrmvrm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8,
  fig.height=5
)
```

```{r setup}
library(tidyverse)
library(vrmvrm)
```

# About

The R package `vrmvrm` is a tidyverse-style toolset for working with spatial data. Unlike most packages working with spatial data in R, we have focused on small-scale data rather than geographic data. This is because the package creator has a background in behavioral data collected virtual and augmented reality studies.

# Quick Overview

(sections, be snazzy)

# Philosophy

The tidyverse 

todyverse ontology (column per variable)

how to deal with 3d vector types are difficult to work with

instead of 3 lines per operation, they 

speak how you think about these operations

requring ggplot - that's a philosophy choice that this package is 50% more valuable if you can see what is being 

# Display

semantic (front, left, right, etc)
uses cowplot to make top / right / front type diagrams
can do projective stuff too!
stereograms?


# Mathematics

we have standard vector mathematics operations.

```{R}
spiral <- data.frame(i = seq(0, 4*pi, 0.01)) %>%
  mutate(
    circular_part = vector3(x=cos(5*i), y=sin(5*i), z=0),
    forward_part = vector3(x=0, y=0, z=i),
    spiral_part = circular_part * i / 4 + forward_part
  )

spiral %>%
  ggplot(aes(x=spiral_part$x, y=spiral_part$y, size=spiral_part$z)) +
  geom_point() + coord_equal()


spiral %>% 
  ggplot(aes(x=spiral_part$z, y=spiral_part$x, color=spiral_part$y)) +
  geom_point() + coord_equal()

```

```{r}
# animated spiral because fun.

anim <- spiral %>% 
  crossing(angle_of_rotation = seq(0, 2*pi-0.01, by=2*pi/10)) %>%
  mutate(spiral_part = rotate(spiral_part, axis=c(1, 0, 0), angle=angle_of_rotation)) %>%
  ggplot(aes(x=spiral_part$z, y=spiral_part$x, color=spiral_part$y)) +
  geom_point() + 
  coord_equal() +
  gganimate::transition_states(angle_of_rotation, state_length=0)

anim

#gganimate::anim_save("goo.gif", anim)
```


# Plotting

# Rotations

There are many ways to specify rotations! We try to work with all of them.

# Spatial Functions

(project, reject, extend, lookat)

# Time and Motion

differentiate vs. integrate

# Settings 

we have conventions! they are tricky! 




