---
title: "vrmvrm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vrmvrm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(vrmvrm)
```

# About

The R package `vrmvrm` is a tidyverse-style toolset for working with spatial data. Unlike most packages working with spatial data in R, we have focused on small-scale data rather than geographic data. This is because the package creator has a background in behavioral data collected virtual and augmented reality studies.

# Quick Overview

# Philosophy

The tidyverse 

todyverse ontology (column per variable)

how to deal with 3d vector types are difficult to work with

instead of 3 lines per operation, they 

speak how you think about these operations

requring ggplot - that's a philosophy choice that this package is 50% more valuable if you can see what is being 

# Mathematics

we have standard vector mathematics operations.

# Rotations

There are many ways to specify rotations! We try to work with all of them.

# Spatial Functions

(project, reject, extend, lookat)

# Time and Motion

differentiate vs. integrate

# Settings 

we have conventions! they are tricky! 




